---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your group name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** |  |
|                                                   |                                                                                                      |
|                                 | 1.135232- Starfield - Sadiki Hamisi                                                                                |
|                                                   |                                                                                                      |
|                               | 2.134782 - Starfield -    Yasmin Choma                                                                                |
|                                                   |                                                                                                      |
|                                | 3.134783- Starfield - Moses Mbugua                                                                                |
|                                                   |                                                                                                      |
|                                 | 4.  ID -Starfield- Glenn Oloo                                                                                |
|                                                   |                                                                                                      |
|                                                   | 5.  ID - Group - Name                                                                                |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   |                                                                                                      |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                              |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                             |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                          |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                           |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

**Note:** the following "*R Markdown*" options have been set as the defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# \<Provide an Appropriate Title Here\>

      LOAD STUDENT DATASET

```{This code is used to load Students Dataset}

library(readr)
student_performance_dataset <-
  read_csv("data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset.CSV",
           col_types =
           cols(
                class_group = col_factor(levels = c("A", "B", "C")),
                gender = col_factor(levels = c("1", "0")),
                YOB = col_date(format = "%Y"),
                regret_choosing_bi = col_factor(levels = c("1", "0")),
                drop_bi_now = col_factor(levels = c("1", "0")),
                motivator = col_factor(levels = c("1", "0")),
                read_content_before_lecture =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                anticipate_test_questions =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                answer_rhetorical_questions =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                find_terms_I_do_not_know =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                copy_new_terms_in_reading_notebook =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                take_quizzes_and_use_results =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                reorganise_course_outline =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                write_down_important_points =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                space_out_revision =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                studying_in_study_group =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                schedule_appointments =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                goal_oriented = col_factor(levels = c("1", "0")),
                spaced_repetition =
                col_factor(levels = c("1", "2", "3", "4")),
                testing_and_active_recall =
                col_factor(levels = c("1", "2", "3", "4")),
                interleaving = col_factor(levels = c("1", "2", "3", "4")),
                categorizing = col_factor(levels = c("1", "2", "3", "4")),
                retrospective_timetable =
                col_factor(levels = c("1", "2", "3", "4")),
                cornell_notes = col_factor(levels = c("1", "2", "3", "4")),
                sq3r = col_factor(levels = c("1", "2", "3", "4")),
                commute = col_factor(levels = c("1", "2", "3", "4")),
                study_time = col_factor(levels = c("1", "2", "3", "4")),
                repeats_since_Y1 = col_integer(),
                paid_tuition = col_factor(levels = c("0", "1")),
                free_tuition = col_factor(levels = c("0", "1")),
                extra_curricular = col_factor(levels = c("0", "1")),
                sports_extra_curricular = col_factor(levels = c("0", "1")),
                exercise_per_week = col_factor(levels = c("0", "1", "2", "3")),
                meditate = col_factor(levels = c("0", "1", "2", "3")),
                pray = col_factor(levels = c("0", "1", "2", "3")),
                internet = col_factor(levels = c("0", "1")),
                laptop = col_factor(levels = c("0", "1")),
                family_relationships =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                friendships = col_factor(levels = c("1", "2", "3", "4", "5")),
                romantic_relationships =
                col_factor(levels = c("0", "1", "2", "3", "4")),
                spiritual_wellnes =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                financial_wellness =
                col_factor(levels = c("1", "2", "3", "4", "5")),
                health = col_factor(levels = c("1", "2", "3", "4", "5")),
                day_out = col_factor(levels = c("0", "1", "2", "3")),
                night_out = col_factor(levels = c("0", "1", "2", "3")),
                alcohol_or_narcotics =
                col_factor(levels = c("0", "1", "2", "3")),
                mentor = col_factor(levels = c("0", "1")),
                mentor_meetings = col_factor(levels = c("0", "1", "2", "3")),
                `Attendance Waiver Granted: 1 = Yes, 0 = No` =
                col_factor(levels = c("0", "1")),
                GRADE = col_factor(levels = c("A", "B", "C", "D", "E"))),
           locale = locale())

View(student_performance_dataset)
```

Contractions of Words From the Student Perfomance Dataset

```{r Your Third Code Chunk}

library(readr)
expand_contractions <- function(doc) {
  doc <- gsub("I'm", "I am", doc, ignore.case = TRUE)
  doc <- gsub("you're", "you are", doc, ignore.case = TRUE)
  doc <- gsub("he's", "he is", doc, ignore.case = TRUE)
  doc <- gsub("she's", "she is", doc, ignore.case = TRUE)
  doc <- gsub("it's", "it is", doc, ignore.case = TRUE)
  doc <- gsub("we're", "we are", doc, ignore.case = TRUE)
  doc <- gsub("they're", "they are", doc, ignore.case = TRUE)
  doc <- gsub("I'll", "I will", doc, ignore.case = TRUE)
  doc <- gsub("you'll", "you will", doc, ignore.case = TRUE)
  doc <- gsub("he'll", "he will", doc, ignore.case = TRUE)
  doc <- gsub("she'll", "she will", doc, ignore.case = TRUE)
  doc <- gsub("it'll", "it will", doc, ignore.case = TRUE)
  doc <- gsub("we'll", "we will", doc, ignore.case = TRUE)
  doc <- gsub("they'll", "they will", doc, ignore.case = TRUE)
  doc <- gsub("won't", "will not", doc, ignore.case = TRUE)
  doc <- gsub("can't", "cannot", doc, ignore.case = TRUE)
  doc <- gsub("n't", " not", doc, ignore.case = TRUE)
  return(doc)
}
```

Loading the required lexicons

```{r Your Fourth Code Chunk}
# file is rendered using knitR
library(tm)
data(hash_nrc_emotions)
nrc <- hash_nrc_emotions
nrc <- nrc %>%
 mutate(word = token, sentiment = emotion) %>%
 select(word, sentiment)
View(nrc)

tidytext::get_sentiments(lexicon = "afinn")
View(afinn)

tidytext::get_sentiments(lexicon = "bing")
View(bing)

tidytext::get_sentiments(lexicon = "loughran")
View(loughran)
```

 Combining Likes Data with NRC Emotion Lexicon

```{r}
evaluation_likes_filtered_nrc <- evaluation_likes_filtered %>%
  full_join(nrc, by = c("Likes (tokenized)" = "word"), suffix = c("", ".nrc"))



evaluation_wishes_filtered_nrc <- evaluation_wishes_filtered %>%
  dplyr::inner_join(nrc,
             by = join_by(`Wishes (tokenized)` == word),
             relationship = "many-to-many")
```

Visualizing Lexicon-Based Sentiment Analysis of Course Evaluation Likes
```{r}
#}
nrc_likes_plot <- evaluation_likes_filtered_nrc %>%
  group_by(sentiment) %>%
  # You can filter by the class group if you wish
  # filter(`Class Group` == "A") %>%
  summarise(word_count = n()) %>%
  ungroup() %>%
  mutate(sentiment = reorder(sentiment, word_count)) %>%
  # `fill = -word_count` is used to make the larger bars darker
  ggplot(aes(sentiment, word_count, fill = -word_count)) +
  geom_col() +
  guides(fill = FALSE) + # Turn off the legend
  blue_grey_theme() +
  labs(x = "Sentiment", y = "Word Count") +
  # scale_y_continuous(limits = c(0, 15000)) + #Hard code the axis limit
  ggtitle("Lexicon-Based Sentiment Analysis of Course Evaluation Likes") +
  coord_flip()
plot(nrc_likes_plot)
```

Creating a Meme with Course Information and Sentiment Analysis Plot
```{r}
img <- "images/SCES-logo-01-blue-grey-bg-with-meme-space.jpg"
# The meme's label can be specified here:
lab <- "The BBT4106: Business Intelligence I course
        taught from 12th April 2023 to 19th July 2023
        by Dr Allan Omondi"
# Overlay the plot on the image and create the meme file
meme(img, lab, "memes/nrc_wishes_plot.jpg", inset = nrc_wishes_plot)
#Read the file back in and display it!
nrc_meme <- image_read("memes/nrc_wishes_plot.jpg")
plot(nrc_meme)
```

Creating Chord Diagram for Sentiment Analysis of Course Evaluation Likes by Group
```{r}
jpeg(filename = "visualizations/nrc_likes_chord.jpeg",
     width = 1920, height = 1080, units = "px", pointsize = 12,
     bg = "transparent", res = 150)

# svg(filename = "visualizations/nrc_likes_chord.svg",
#     width = 8.5, height = 8.5, pointsize = 12,
#     bg = "transparent")

# pdf("visualizations/nrc_likes_chord.pdf",
#     width = 8.5, height = 8.5,
#     bg = "transparent", pagecentre = TRUE, paper = "A4")

grid_col <- c("A" = blue_grey_colours_11[1],
              "B" = "#f3c487",
              "C" = blue_grey_colours_11[5])

nrc_likes_chord <-  evaluation_likes_filtered_nrc %>%
  # filter(decade != "NA" & !sentiment %in% c("positive", "negative")) %>%
  count(sentiment, `Class Group`) %>%
  group_by(`Class Group`, sentiment) %>%
  summarise(sentiment_sum = sum(n)) %>%
  filter(sentiment_sum > 10) %>%
  mutate(sentiment = reorder(sentiment, sentiment_sum)) %>%
  ungroup()

circos.clear()
# Set the gap size
circos.par(gap.after = c(rep(5, length(unique(nrc_likes_chord[[1]])) - 1), 15,
                         rep(5, length(unique(nrc_likes_chord[[2]])) - 1), 15))

chordDiagram(nrc_likes_chord, grid.col = grid_col, transparency = .2)
title("Lexicon-Based Sentiment Analysis of Course Evaluation Likes per Group")

# To close the device used to create either the PNG, JPEG, SVG, or PDF.
dev.off()
```

Creating a Radar Chart of Sentiment Counts per Group
```{r}
nrc_likes_per_sentiment_per_group_radar <- # nolint
  evaluation_likes_filtered_nrc %>%
  group_by(`Class Group`, sentiment) %>%
  count(`Class Group`, sentiment) %>%
  select(`Class Group`, sentiment, sentiment_count = n)

View(nrc_likes_per_sentiment_per_group_radar)
```


**etc.** as per the lab submission requirements.
